### 2015-01-13 paper/Content/solution.tex
Minor corrections
minor changes
typos

The prototype Android app, developed for this paper, is a simple weather app. It is able to show the current weather data for a location including temperature, humidity and wind. For retrieving this data, the app connects to the remote \emph{application programming interface} (API) of \emph{openweathermap.org}, a free-to-use service for retrieving weather data. The app also manages a list of favourite locations. Locations can either be specified using a free-text search field or by pointing locations on a map, for which the \emph{Google Maps} API was used.

@@

Each activity object has an presenter object associated, implementing the \texttt{Presenter} interface. On the other hand, the presenter object has a reference to the activity object. View related actions, like a click on a button, cause handler functions inside the \texttt{Activity} class being called. Those handler functions do nothing more than executing corresponding actions on the presenter object.

>>>>

\IEEEPARstart{T}{he} prototypical Android app, developed for this paper, is a simple weather app. It is able to show the current weather data for a location including temperature, humidity and wind. For retrieving this data, the app connects to the remote \emph{application programming interface} (API) of \emph{openweathermap.org}, a free-to-use service for retrieving weather data. The app also manages a list of favourite locations. Locations can either be specified using a free-text search field or by pointing locations on a map, for which the \emph{Google Maps} API was used.

@@

Each activity object has a presenter object associated, implementing the \texttt{Presenter} interface. On the other hand, the presenter object has a reference to the activity object. View related actions, like a click on a button, cause handler functions inside the \texttt{Activity} class being called. Those handler functions do nothing more than executing corresponding actions on the presenter object.
